### 2022-04-22 paper/ase22/experiment.tex
exp

In this section, we present experiments to evaluate the effectiveness
of our proposed evaluation methodology. In particular, we address the
following research questions:

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: How effective is our proposed evaluation model
  for finding failures given a linguistic capability?
\item \label{rq:two}: Can \tool be useful to find root of bug in the
  NLP models?
\item \label{rq:three}: How effective is our new test case generation
  using \cfg expansion? % ablation study
\end{enumerate}

For answering \ref{rq:one} and \ref{rq:two}, we generate test cases
and use them for evaluating model on linguistic capabilities. In this
experiment, We assess the ability to find failures by anlyzing model's
performance on the generated test cases. We also measure the diversity
among the generated test cases using similarites among them. Next, we
answer \ref{rq:three} by retraining \sa model with generated test
cases and measuring performances. The idea behind this is that more
comprehensive inputs becomes closer to real-world distribution and
addresses more type of errors.  Therefore, it leads to improve the
model performance. In this experiment, We retrain the model and
compare performances of the retrained model. Not only that, we conduct
ablation study of \cfg expansion to understand the its impact in our
approach.

>>>>

In this section, we present experiments to evaluate the effectiveness
of our proposed evaluation methodology. In particular, we address the
following research questions (RQs):

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: Can \tool find different bugs from \Cklst?
\item \label{rq:two}: Can the \tool generated testcases have stronger
  generalization ability to test NLP models?
\item \label{rq:three}: Can \tool be useful to find root of bug in the
  NLP models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

To answer the RQs, we need to show: (i) effect of testcase
distribution on finding bugs; (ii) degree of execution of a NLP model
on testcases; and (iii) ability to guide to find cause of bug in a NLP
model. First, evaluation on distribution of generated testcase more
equivalent to real world estimates model performance in practical use
more accurately. It means more various bugs from the input
distribution are likely to be detected.  On the other hand, limited
distribution only represents narrow or uncommon portion of real world,
and it leads to detect bugs within the restricted range. Therefore,
demonstrating bugs detected from testcases distribution can answer the
RQ~\ref{rq:one}. Second,

we generate test cases
and use them for evaluating model on linguistic capabilities. In this
experiment, We assess the ability to find failures by anlyzing model's
performance on the generated test cases. We also measure the diversity
among the generated test cases using similarites among them. Next, we
answer \ref{rq:three} by retraining \sa model with generated test
cases and measuring performances. The idea behind this is that more
comprehensive inputs becomes closer to real-world distribution and
addresses more type of errors.  Therefore, it leads to improve the
model performance. In this experiment, We retrain the model and
compare performances of the retrained model. Not only that, we conduct
ablation study of \cfg expansion to understand the its impact in our
approach.

### 2022-04-22 paper/ase22/related.tex
exp

\begin{comment}
Not only that, model is evaluated on different aspects such as
robustness of the model on adversarial
sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial},
fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
consistancy~\cite{ribeiro2019consistencyeval}, prediction
interpretations~\cite{ribeiroSG16lime} and interactive error
analysis~\cite{wu2019errudite}. Especially, \Cklst implements
behavioral testing methodolgy for evaluating multiple linguistic
capabilities of NLP model~\cite{marcoACL2020checklist}. \Cklst
introduces input-output behaviors of linguistic capabilities and
generates behavior-guided inputs for validating the behaviors. It
provides comprehensive behavioral testing of NLP models through a
number of generated inputs. However, the approach only relies on
manually generated input templates, thus the template generation
becomes expensive and time consuming. In addition, the generated
templates are selective and often too simple, and it is limited to
provide restricted evaluation of linguistic capabilities. Thus, it
does not garauntee the comprehensive evaluation.
\end{comment}

>>>>

\begin{comment}

  %% On the subject of the limitation of traditional testing paradigm, a
%% number of methods have been proposed. First, multiple diagnostic
%% datasets for evaluating NLP model were introduced for obtaining
%% generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
%% that, model is evaluated on different aspects such as robustness of
%% the model on adversarial
%% sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
%%   rychalska2019wildnlp,iyyer2018adversarial},
%% fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
%% consistancy~\cite{ribeiro2019consistencyeval}, prediction
%% interpretations~\cite{ribeiroSG16lime} and interactive error
%% analysis~\cite{wu2019errudite}. Especially, \Cklst implements
%% behavioral testing methodolgy for evaluating multiple linguistic
%% capabilities of NLP model~\cite{marcoACL2020checklist}. \Cklst
%% introduces input-output behaviors of linguistic capabilities and
%% generates behavior-guided inputs for validating the behaviors. It
%% provides comprehensive behavioral testing of NLP models through a
%% number of generated inputs. However, the approach only relies on
%% manually generated input templates, thus the template generation
%% becomes expensive and time consuming. In addition, the generated
%% templates are selective and often too simple, and it is limited to
%% provide restricted evaluation of linguistic capabilities. Thus, it
  %% does not garauntee the comprehensive evaluation.

Not only that, model is evaluated on different aspects such as
robustness of the model on adversarial
sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial},
fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
consistancy~\cite{ribeiro2019consistencyeval}, prediction
interpretations~\cite{ribeiroSG16lime} and interactive error
analysis~\cite{wu2019errudite}. Especially, \Cklst implements
behavioral testing methodolgy for evaluating multiple linguistic
capabilities of NLP model~\cite{marcoACL2020checklist}. \Cklst
introduces input-output behaviors of linguistic capabilities and
generates behavior-guided inputs for validating the behaviors. It
provides comprehensive behavioral testing of NLP models through a
number of generated inputs. However, the approach only relies on
manually generated input templates, thus the template generation
becomes expensive and time consuming. In addition, the generated
templates are selective and often too simple, and it is limited to
provide restricted evaluation of linguistic capabilities. Thus, it
does not garauntee the comprehensive evaluation.
\end{comment}
